Explorations to Optimize the Parareal Algorithm \\to Solve ODEs in Given Applications

### 2014-12-10 paper.tex

When $k = 2$ and $Q = 100$, for maximal speedup (fewest iterations) of $S(n) = \frac{203n}{3n+200} \approx 67$

When $k = 10$ and $Q = 100$, for more iterations and less error, we'd see an Amdahl bounded max speedup of $S(n) = \frac{1011n}{11n+1000} \approx 91$

@@

WESLEY ENDED HERE, BEFORE THIS IS WESLEY APPROVED

@@

\subsection{Comparison to Serial with $g_{\textnormal{fine}}$ as Higher Order Methods}

IDEALLY WE SHOW THE SAME GRAPHS AS THE ABOVE WITH ALL THE VARIATIONS TESTED

@@

Note that each processor receives information from only those adjacent to it; that is, the top left processor in the graphic does not communicate directly with the bottom right processor in the graphic. Rather, information is passed only along shared boundary points to propagate the wave equation. We run this code for three different grid sizes: $128\times 128$, $256\times 256$, and $512\times 512$, in both serial and parallel.

@@

\begin{center}
\begin{tabular}{|c|c|} \hline
($N_x, N_y$) & Time (seconds)\\ \hline
(128, 128) & 0.987\\ \hline
(256, 256) & 7.889\\ \hline %real
(512, 512) & 63.913\\ \hline %real
\end{tabular}
\end{center}

@@

\begin{center}
\begin{tabular}{|c|c|c|c|c|} \hline
($N_x, N_y$) & $P_x$ & $P_y$ & Time (sec) \\ \hline
(128, 128) & 2 & 2 & (still queued on Odyssey)\\ \hline
(128, 128) & 4 & 2 & 2.31 \\ \hline
(128, 128) & 4 & 4 & (still queued on Odyssey) \\ \hline
(128, 128) & 8 & 8 & (still queued on Odyssey) \\ \hline
(256, 256) & 2 & 2 & 2.57 \\ \hline %real
(256, 256) & 4 & 2 & 11.32 \\ \hline
(256, 256) & 4 & 4 & 13.65 \\ \hline
(256, 256) & 8 & 8 & 17.44 \\ \hline
(512, 512) & 2 & 2 & (still queued on Odyssey)\\ \hline
(512, 512) & 4 & 2 & (still queued on Odyssey)\\ \hline
(512, 512) & 4 & 4 & (still queued on Odyssey)\\ \hline %check
(512, 512) & 8 & 8 & (still queued on Odyssey) \\ \hline %check
\end{tabular}
\end{center}

>>>>

When $k = 2$ and $Q = 100$, for maximal speedup (fewest iterations) of:
\[
\begin{aligned}
S(n) &= \frac{203n}{3n+200} \\
\lim_{n\to \infty}S(n) &\approx 67
\end{aligned}
\]

When $k = 10$ and $Q = 100$, for more iterations and less error, we'd see an Amdahl bounded max speedup of 
\[
\begin{aligned}
S(n) &= \frac{1011n}{11n+1000} \\
\lim_{n\to \infty}S(n) &\approx 91
\end{aligned}
\]

@@

@@

@@

Note that each processor receives information from only those adjacent to it; that is, the top left processor in the graphic does not communicate directly with the bottom right processor in the graphic. Rather, information is passed only along shared boundary points to propagate the wave equation. We run this code for two different grid sizes: $256\times 256$ and $512\times 512$, in both serial and parallel.

@@

\begin{center}
\begin{tabular}{|c|c|} \hline
($N_x, N_y$) & Time (seconds)\\ \hline
%(128, 128) & 0.987\\ \hline
(256, 256) & 7.889\\ \hline %real
(512, 512) & 63.913\\ \hline %real
\end{tabular}
\end{center}

@@

\begin{center}
\begin{tabular}{|c|c|c|c|c|} \hline
($N_x, N_y$) & $P_x$ & $P_y$ & Time (sec) & Speedup \\ \hline
%(128, 128) & 2 & 2 & (still queued on Odyssey) & \\ \hline
%(128, 128) & 4 & 2 & (still queued on Odyssey) & \\ \hline %check
%(128, 128) & 4 & 4 & (still queued on Odyssey) & \\ \hline
%(128, 128) & 8 & 8 & (still queued on Odyssey) & \\ \hline
(256, 256) & 2 & 2 & 2.57 & 3.07\\ \hline %real
(256, 256) & 4 & 2 & 11.32 & \\ \hline %check
(256, 256) & 4 & 4 & 13.65 & \\ \hline %check
(256, 256) & 8 & 8 & 17.44 & \\ \hline %check
(512, 512) & 2 & 2 & 39.65 & 1.61\\ \hline %real
(512, 512) & 4 & 2 & (still queued on Odyssey)& \\ \hline
(512, 512) & 4 & 4 & (still queued on Odyssey)&\\ \hline %check
(512, 512) & 8 & 8 & (still queued on Odyssey)&\\ \hline %check
\end{tabular}
\end{center}
